Variational Monte Carlo on Bosonic Systems

### 2018-04-04 project_1/article/article.tex
Move references before appendix
Align abstract
Start on MC integration

%\begin{widetext}

%\end{widetext}

@@

        To get around\footnote{Not exactly \emph{get around} per se, but make
        the problem solvable at all.} the trouble of evaluating the integral we
        employ the method of Monte Carlo integration.

@@

@@

\bibliography{references}

>>>>

@@

        To get around\footnote{Not exactly \emph{get around} per se, but make
        the problem solvable at all.} the trouble of evaluating the
        multidimensional-integral we employ the method of Monte Carlo
        integration.

@@

\bibliography{references}
\clearpage

@@
